---
title: "linreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab4)
```

## Introduction

This package fits multiple linear regression models with `linreg()`,
using ordinary least squares. Here we use the `iris` dataset.

## Fitting a model

```{r}
mod <- linreg(Petal.Length ~ Species, data = iris)
```

## Methods

`print()` shows the call and the coefficients:

```{r}
print(mod)
```

`coef()` returns the coefficients as a named vector:

```{r}
coef(mod)
```

`resid()` returns the residuals and `pred()` the predicted values
(first six shown):

```{r}
head(resid(mod))
head(pred(mod))
```

`summary()` shows the standard errors, t-values, p-values, the residual
standard error and the degrees of freedom:

```{r}
summary(mod)
```

`plot()` draws Residuals vs Fitted and Scale-Location:

```{r, fig.height = 4, fig.width = 6}
plot(mod)
```
